Designing Robust Controllers With $H_{\infty}$ Performance Using Frequency-Domain Data

### 2017-02-13 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
Update Draft.tex
updated file

\section{Conclusion} \label{sec:conclusion}
Robust performance can be accomplished by considering the $\mathcal{H}_{\infty}$ control problem. By presetting a frequency grid, an optimization problem can be formulated to minimize the upper-bound of the robust performance condition and solve a finite amount of constraints in the frequency-domain. In this paper, a Non-Death-Penalty approach has been implemented to solve an unconstrained $\mathcal{H}_{\infty}$ problem; the solution to this problem was obtained by realizing a PSO algorithm. From the examples considered in this paper, it is evident that the solutions obtained from the PSO algorithm generate favorable closed-loop responses (with respect to the other methods considered in this paper). In terms of performance, the convex optimization algorithm produces a solution that is comparable to that of the PSO. From the simulation examples, it can be deduced that the solution obtained from the convex optimization algorithm is a good approximation to the solution obtained from the original problem. For further research, it will be desired to investigate how the solution obtained from the PSO algorithm with the $\epsilon$-level comparisons correlates with the solutions obtained in this work.

>>>>

\section{Conclusion} \label{sec:conclusion}
A frequency-domain approach has been implemented in order to design robust controllers that achieve $\mathcal{H}_{\infty}$ performance. With the proposed method, it has been shown that the solution to the $\mathcal{H}_{\infty}$ problem converges monotonically to the optimal solution with the order of the basis function $F$ approaches infinity. This solution is obtained by considering an optimization problem which guarantees the stability of the closed-loop system. The optimization problem is converted from an SIP problem to an SDP problem by gridding the frequency vector over a finite interval. The simulation examples show that the proposed approach achieves the optimal performance for a given controller order without any conservatism. For future work, it will be desired to implement this method for multi-input-multi-output (MIMO) systems and systems with controllers that possess multiple degrees-of-freedom.
